Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
Keep animal and seed locations in one df

```{r message=FALSE}
library(dplyr)
library(ggplot2)
```

@@

# Determine where the seeds are dropped based on the animal's location.
seed_loc <- data.frame(seed_id = 1:nseeds, time = grt)
seed_loc <- merge(animalTraj, seed_loc, by = "time")
seed_loc$dispersal <- sqrt(seed_loc$xloc^2 + seed_loc$yloc^2)

@@

animalTraj %>% 
  ggplot(., aes(x = xloc, y=yloc)) +
  geom_path() +
  geom_point(data=seed_loc, aes(x = xloc, y = yloc)) +
  geom_point(aes(x = x_m, y = y_m), color = "Red") + # Mean location of seeds

>>>>

```{r message=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
```

@@

animalTraj %>% 
  left_join(., data.frame(s.id = 1:nseeds, time = grt)) %>% 
  mutate(disp = sqrt(xloc^2+yloc^2)) -> df

@@

df %>% 
  ggplot(., aes(x = xloc, y=yloc)) +
  geom_path() +
  geom_point(data = df %>% drop_na(s.id), aes(x = xloc, y = yloc)) +
  geom_point(aes(x = x_m, y = y_m), color = "Red") + # Mean location of seeds
